Modelling spatial structure in small-area estimation

### 2022-07-31 src/docs_paper/preamble.tex
Work on manuscript and simulation study
Iterate manuscript forward

\RequirePackage{amsthm,amsmath,amsfonts,amssymb}
\RequirePackage{bm}
\RequirePackage{enumerate}
\RequirePackage{enumitem}
\RequirePackage{tabularx}
\RequirePackage{adjustbox}
\RequirePackage{tikz}
\RequirePackage{bbm}
\RequirePackage{lscape}
\RequirePackage{booktabs}
\RequirePackage{longtable}
\RequirePackage{lscape}
\RequirePackage{pifont}
\usepackage{footnote}

@@

>>>>

\RequirePackage{amsthm,amsmath,amsfonts,amssymb}
\RequirePackage{bm}
\RequirePackage{enumerate}
\RequirePackage{enumitem}
\RequirePackage{tabularx}
\RequirePackage{adjustbox}
\RequirePackage{tikz}
\RequirePackage{bbm}
\RequirePackage{lscape}
\RequirePackage{booktabs}
\RequirePackage{longtable}
\RequirePackage{lscape}
\RequirePackage{pifont}
\RequirePackage[margin=1in]{geometry}
\usepackage{footnote}

@@

\definecolor{lightblue}{HTML}{56B4E9}
\definecolor{lightgreen}{HTML}{009E73}
\definecolor{lightorange}{HTML}{E69F00}
\definecolor{lightgrey}{HTML}{E6E6E6}

\newcommand{\lightblueline}{\raisebox{2pt}{\tikz{\draw[-,lightblue,solid,line width = 3pt](0,0) -- (2mm,0);}}}
\newcommand{\lightgreenline}{\raisebox{2pt}{\tikz{\draw[-,lightgreen,solid,line width = 3pt](0,0) -- (2mm,0);}}}
\newcommand{\lightorangeline}{\raisebox{2pt}{\tikz{\draw[-,lightorange,solid,line width = 3pt](0,0) -- (2mm,0);}}}
\newcommand{\lightgreyline}{\raisebox{2pt}{\tikz{\draw[-,lightgrey,solid,line width = 3pt](0,0) -- (2mm,0);}}}
